---
title: "Lesson 8"
author: "Team Wij doen MEE"
date: "19 januari 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r main, include=FALSE}
source("main.R")
```

## Question 1
### Paired plot of all bands

First outliers of the bands were removed from the histograms and VCF max was set to 100. 

```{r, include = TRUE}
GewataB1[GewataB1 > 750]   <- NA
GewataB2[GewataB2 > 1000]  <- NA
GewataB3[GewataB3 > 1250]  <- NA
GewataB4[GewataB4 > 4000]  <- NA
GewataB5[GewataB5 > 3500]  <- NA
GewataB7[GewataB7 > 2200]  <- NA
vcfGewata[vcfGewata > 100] <- NA
```

To check the correlation the bands were bricked and a pairs plot was used.

```{r GewataBrick, include = TRUE}
pairs(GewataBrick)

```

VCF seems to be quite well correlated with all bands except band 4.

## Question 2
### Model


```{r vcfmodel, include=TRUE}
summary(vcfmodel)
```
All bands are significant and therefore we use all bands in the VCF prediction.


## Question 3
### Plot of the predicted and original VCF rasters
```{r vcfpred_map, r vcfGewata, echo = FALSE}
levelplot(stack(vcfpred_map, vcfGewata), main=c("Predicted VCF","Actual VCF"), 
          col.regions=rev(grDevices::terrain.colors(100)), axes=T)
```

The prediction is quite accurate, some small differences are visible.
Extreme values that were out of range (0 <= range <= 100) have been set to NA, this causes
more white spots to be visible in the predicted VCF.


## Question 4
### Calculation of the RMSE between prediction and actual VCF

```{r rmse_avg, include = TRUE, echo = FALSE}
paste("The average RMSE of the area is", rmse_avg)
```

Plotted it looks like this:

```{r rmse_map, include=TRUE, echo = FALSE}
plot(rmse_map, main="RMSE", axes=TRUE)
```

## Question 5
### RMSE of the 3 classes in the trainingpolygons


```{r rmse_classes, include = TRUE, echo = TRUE}
rmse_classes
```













